### 2019-08-10 simulation.tex
General touching up

According to the QCD factorization theorem, the dominant contribution to the cross section $\sigma_{X}$ of such a process is given by (see e.g.~\cite{ref:BargerPhillips})
\begin{equation}
\sigma_{X} = \sum_{i,j}\int \! dx_{1}dx_{2} \, f_{i}(x_{1}, \mu_{F}^{2})f_{j}(x_{2}, \mu_{F}^{2})\sigma_{i,j \to X}
\label{eq:qcd_factorization}
\end{equation}
where $i,j$ specify the types of the hard scattering partons, and $\sigma_{i,j \to X}$ is the cross section for the partonic process
\begin{equation}
i + j \to X + rest
\label{eq:parton_interaction}
\end{equation}
which can be computed to a desired order using Feynman diagrams\footnote{Here $rest$ is a collection of quarks and gluons
that eventually fragment into final-state hadrons.}. The energy scale $\mu_{F}$ is called the factorization scale.
The value of $\alpha_\mathrm{S}$, which appears in perturbative expansions of $\sigma_{i,j \to X}$, is governed by another energy scale $\mu_{R}$ called
the renormalization scale\footnote{As the characteristic
energy scale increases, the effective value of $\alpha_\mathrm{S}$ decreases. This is in contrast to the fine structure ``constant'' $\alpha$,
whose value increases with increasing energy.}.
The coefficients of $\alpha_\mathrm{S}$ in such perturbative expansions also depend on $\mu_{F}$ and $\mu_{R}$,
in such a way as to completely cancel any $\mu_{F}, \mu_{R}$ dependence in the exact formula for the total cross section $\sigma_{X}$~\cite{ref:0034-4885/70/1/R02}.

@@

However, the full dynamics of a \Pp\Pp\ interaction and subsequent interactions of the products with the CMS detector do not admit simple solutions.
These and other integrals over probability distributions may be estimated
via the Monte Carlo (MC) method. Many random events\footnote{``Monte Carlo'' alludes to an eponymous casino in Monaco.}
are generated according to known probability distributions,
and the integrand (e.g. some reconstructed kinematic quantity) is evaluated for each event.
The sum of the integrand values for each event within a given kinematic region,
divided by the total number of events generated, gives an estimate of the integral within that region (e.g. the
content of a bin in a histogram).

@@

\section{Parton showering and hadronization} \label{sec:simulation_parton_shower_hadronization}
The output of the hard collision, $X + rest$, continues to evolve as it exits the interaction point.
For example, high-energy quarks and gluons will tend to radiate other high-energy quarks and gluons in a cascading process
known as a parton shower, dispersing their energy as they do so. The energies of the showering partons begin at the hard interaction energy scale
and go down to the hadronization scale (${\lesssim}10\unit{GeV}$). Above this energy scale, $\alpha_\mathrm{S}$ is less than $O(1)$, and so the parton
shower process admits a perturbative analysis in the theory of QCD.
The statistical behavior of parton showering is governed by Sudakov form factors derived from the DGLAP equations~\cite{ref:0034-4885/70/1/R02}.

>>>>

According to the QCD factorization theorem, the dominant contribution to the cross section $\sigma_{X}$ of such a process is given by (see e.g.~\cite{ref:BargerPhillips})
\begin{equation}
\sigma_{X} = \sum_{i,j}\int \! dx_{1}dx_{2} \, f_{i}(x_{1}, \mu_{F}^{2})f_{j}(x_{2}, \mu_{F}^{2})\sigma_{i,j \to X}
\label{eq:qcd_factorization}
\end{equation}
where $i,j$ specify the types of the hard scattering partons, and $\sigma_{i,j \to X}$ is the cross section for the partonic process
\begin{equation}
i + j \to X + rest
\label{eq:parton_interaction}
\end{equation}
which can be computed to a desired order using Feynman diagrams\footnote{Here $rest$ is a collection of quarks and gluons
that eventually fragment into final-state hadrons.}. The energy scale $\mu_{F}$ is called the \textit{factorization scale}.
The value of $\alpha_\mathrm{S}$, which appears in perturbative expansions of $\sigma_{i,j \to X}$, is governed by another energy scale $\mu_{R}$ called
the \textit{renormalization scale}\footnote{As the characteristic
energy scale increases, the effective value of $\alpha_\mathrm{S}$ decreases. This is in contrast to the fine structure ``constant'' $\alpha$,
whose value increases with increasing energy.}.
The coefficients of $\alpha_\mathrm{S}$ in such perturbative expansions also depend on $\mu_{F}$ and $\mu_{R}$,
in such a way as to completely cancel any $\mu_{F}, \mu_{R}$ dependence in the exact formula for the total cross section $\sigma_{X}$~\cite{ref:0034-4885/70/1/R02}.

@@

However, the full dynamics of a \Pp\Pp\ interaction and subsequent interactions of the products with the CMS detector do not admit simple solutions.
These and other integrals over probability distributions may be estimated
via the \textit{Monte Carlo} (MC) method. Many random events\footnote{``Monte Carlo'' alludes to an eponymous casino in Monaco.}
are generated according to known probability distributions,
and the integrand (e.g. some reconstructed kinematic quantity) is evaluated for each event.
The sum of the integrand values for each event within a given kinematic region,
divided by the total number of events generated, gives an estimate of the integral within that region (e.g. the
content of a bin in a histogram).

@@

\section{Parton showering and hadronization} \label{sec:simulation_parton_shower_hadronization}
The output of the hard collision, $X + rest$, continues to evolve as it exits the interaction point.
For example, high-energy quarks and gluons will tend to radiate other quarks and gluons in a cascading process
known as a \textit{parton shower}, dispersing their energy as they do so. The energies of the showering partons begin at the hard interaction energy scale
and go down to the hadronization scale (${\lesssim}10\unit{GeV}$). Above this energy scale, $\alpha_\mathrm{S}$ is less than $O(1)$, and so the parton
shower process admits a perturbative analysis in the theory of QCD.
The statistical behavior of parton showering is governed by Sudakov form factors derived from the DGLAP equations~\cite{ref:0034-4885/70/1/R02}.
